### 2017-05-31 doc/related.tex
related

While this paper was under review, a number of articles appeared which also 
investigate linguistic representations in LSTM architectures. In an 
approach similar to ours, \namecite{li2016understanding} study the contribution of 
individual input tokens as well as hidden units and word embedding dimensions 
by erasing them from the representation and analyzing how this affects the model.
\namecite{adi2016fine} take an alternative approach by introducing prediction tasks 
to analyze information encoded in sentence embeddings about sentence length, 
sentence content and word order. Finally, \namecite{linzen2016assessing} examine 
the acquisition of long-distance dependencies through the study of number agreement 
in different variations of an LSTM model with different objectives (number prediction, 
grammaticality judgment, and language modeling). Their results show that such dependencies 
can be captured with very high accuracy when the model receives a strong supervision 
signal (that is, whether the subject is plural or singular), but simple language models still capture 
the majority of test cases. All these models focus on text-based tasks and do not take other 
modalities such as visual input into account.

>>>>

While this paper was under review, a number of articles appeared which also 
investigate linguistic representations in LSTM architectures. In an 
approach similar to ours, \namecite{li2016understanding} study the contribution of 
individual input tokens as well as hidden units and word embedding dimensions 
by erasing them from the representation and analyzing how this affects the model.
They focus on text-only tasks and do not take other 
modalities such as visual input into account.
\namecite{adi2016fine} take an alternative approach by introducing prediction tasks 
to analyze information encoded in sentence embeddings about sentence length, 
sentence content and word order. 
Finally, \namecite{linzen2016assessing} examine 
the acquisition of long-distance dependencies through the study of number agreement 
in different variations of an LSTM model with different objectives (number prediction, 
grammaticality judgment, and language modeling). Their results show that such dependencies 
can be captured with very high accuracy when the model receives a strong supervision 
signal (that is, whether the subject is plural or singular), but simple language models still capture 
the majority of test cases. While they focus on an in-depth analysis of a single phenomenon, in our work
we are interested in methods which make it possible to uncover a broad variety of patterns of bebavior in RNNs.
